Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
complititude [fixed]

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.

This is why for answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an application used mainly in IT departments and software development), or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}). In this case, it is maybe in order a certain clarification. While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completitude. But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle. So the answer to this question must be understood in two different ways: their preference for the {\em source} of the technology (university, any company) as well as the {\em type} of technology (instant, app based messaging systems vs. web-based systems integrated in another learning management system).

>>>>

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.

This is why for answering RQ1, teachers were queried about whether they use messaging apps in their classes, specifically, Telegram, WhatsApp, Slack (an application used mainly in IT departments and software development), or any other messaging app, and whether they use messaging apps provided by their academic institution (see Table \ref{tab:use_messapps}). In this case, it is maybe in order a certain clarification. While we had in mind, as indicated by the possible answers, instant messaging applications when making this question, we included these institution-provided applications mainly for completion. But it should be noted that, in most cases, they are not {\em instant} messaging apps in the way Telegram or Facebook Messenger are; in most cases they are messaging facilities provided by learning management systems such as (usually) Moodle. So the answer to this question must be understood in two different ways: their preference for the {\em source} of the technology (university, any company) as well as the {\em type} of technology (instant, app based messaging systems vs. web-based systems integrated in another learning management system).
